Manuscript for MADA Project

### 2023-04-24 products/Manuscript.qmd
Updates

## Vaccination Trends of the Black Community for Each Zip Code 
```{r}
knitr::include_graphics("../results/31701_total_black_vax.png")
```

>>>>

## Vaccination Trends of the Black Community for Each Zip Code

The was no noticiable increase of vaccination rate for

```{r}
knitr::include_graphics("../results/plot_31701_total_black_vax_rate.png")
```
